Learning how to act: making good decisions with machine learning

### 2017-09-20 thesis/offcuts_chapter6.tex
fixes references
addresses Tiberio's comments

\section*{Questions for Tor}
- How do I fix the page numbering in my thesis?
- How does one derive the regret decompostion
- Any suggestions on reviewers for my thesis (or people who should not be reviewers)
- Who else do I need to cite in my bandits chapter?

\chapter*{Todo}
\begin{enumerate}
\item Write a talk - include slide on causal inference without do
\item Check what I actually have to do to submit
\item Add something about Granger causality - does this belong in chapter 2 or chapter 3?
\item Sell my PhD as two key contribution. 1) A technical one, the other educational and unifying (across viewpoints)
\item Add a chapter in 'PhD prose' making some statement about the intersection of prediction and causality. When is a problem causal, what bounds does predictive accuracy give on causal models? To what degree is predictive accuracy a metric on which causal models can be judged? 
\item Benchmark estimation algorithms
\item clarify causal interpretation of Dirichlet models
\item Empirical evaluation of bandit algorithms (updated to include latest suggestions). Maybe a proper software bench marking solution?
\item If comparing bandit performance, it would be interesting to include some that violate the stochastic bandit assumption. For example, if the rewards change slowly over time or jump suddenly a limited number of times, or with some small probability. 
\item Does defining causality in term of the truncated product formula ensure that a causal Bayesian network is unique? It would seem no, one can ad links (although this is hardly useful) - seems like there is no reverse condition. 
\item Statistisian/Econometricians and computer science seem to use different definitions of optimality (bandits vs efficient estimators). Clarify this - would make a good blog post I think. 
\end{enumerate}

>>>>

\section*{Questions for Tor}
- How does one derive the regret decompostion
- Any suggestions on reviewers for my thesis (or people who should not be reviewers)
- Who else do I need to cite in my bandits chapter?

\chapter*{Todo}
\begin{enumerate}
Clarify Cheng's Questions - is there a mechanical method to go from one framework to another, does it matter if variables are discrete or continuous. \todo{}

\item Write a talk - include slide on causal inference without do
\item Check what I actually have to do to submit
\item Add something about Granger causality - does this belong in chapter 2 or chapter 3?
\item Sell my PhD as two key contribution. 1) A technical one, the other educational and unifying (across viewpoints)
\item Add a chapter in 'PhD prose' making some statement about the intersection of prediction and causality. When is a problem causal, what bounds does predictive accuracy give on causal models? To what degree is predictive accuracy a metric on which causal models can be judged? 
\item Benchmark estimation algorithms
\item clarify causal interpretation of Dirichlet models
\item Empirical evaluation of bandit algorithms (updated to include latest suggestions). Maybe a proper software bench marking solution?
\item If comparing bandit performance, it would be interesting to include some that violate the stochastic bandit assumption. For example, if the rewards change slowly over time or jump suddenly a limited number of times, or with some small probability. 
\item Does defining causality in term of the truncated product formula ensure that a causal Bayesian network is unique? It would seem no, one can ad links (although this is hardly useful) - seems like there is no reverse condition. 
\item Statistisian/Econometricians and computer science seem to use different definitions of optimality (bandits vs efficient estimators). Clarify this - would make a good blog post I think. 
\end{enumerate}
